\subsection{Unresolved goal}

{``\textit{In a few minutes I am going to ask you to focus your attention on a problem or difficulty you have that{}'s
still unresolved and bothering you --so this is an ongoing and unresolved concern that has been repeatedly coming in to
your mind }\textbf{\textit{over recent weeks}}\textit{, causing you to feel negative, sad, down or stressed.}}

{\textit{Examples of the kind of difficulty that I would like you think about are... }}
{\textit {
\begin{itemize}
\item {An ongoing concern about an important relationship, which you have recently felt that you should be managing better.}
\item {A recent negative event and its impact upon how you have been feeling over the past few weeks.}
\item {Concerns over recent weeks that you have failed to achieve a goal that is of personal importance to you.}
\item {Feelings over recent weeks that you disappoint someone who means a lot to you.}
\item {Feelings over recent weeks that you do not compare favorably to other people with respect to an area of functioning that
is important to you.}
\end{itemize}
}}
\textit{These are just example topics. The problem or difficulty that
you think about must be personally meaningful, something that has been
repeatedly troubling you recently and that you have not resolved, that
is, it still bothers you and still comes repeatedly to mind. Although
I'll ask you to describe the problem or difficulty, I won't require you
to provide any specific details about it that you're not comfortable
with sharing. Nevertheless, it is important to choose a real problem
that is genuinely troubling you. The problem or difficulty should not
be something temporary or likely to be completely resolved over the next
5 weeks. For example, \enquote{Writing my draft paper whose deadline is
in 3 weeks}would not be appropriate.}

\textbf{Give unresolved problem/concern sheet to P and allow them time to read it.}

[\textcolor[rgb]{0.0,0.5019608,0.0}{After 2 minutes}] \textit{Can you think of a problem or difficulty of
this kind to think about? }

If no remind participant of examples and give them some time to think of a suitable topic. If yes proceed as follows:

\textit{Would you mind telling me very briefly what the problem is
so that I can confirm it is suitable? You don't need to use specific
names of people or places, or reveal any information that you are not
comfortable with.}

\textit{Is this problem likely to remain unresolved over the next 5 weeks?}

If not an appropriate topic remind participant of the type of concern that we are interested in and the examples and
give further time to try to identify a concern of this kind. Repeat until suitable, then ...

\textit{Now I'd like you to write a statement that will be used throughout
the study to remind you of this unresolved problem or concern. Again,
you don't need to reveal any information that you are not comfortable
with in the statement. It's sufficient that it is enough to remind you
of your unresolved problem or concern. When you have done that, please
evaluate the difficulty using the scales provided.}

\subsection{Goal ratings}

\textbf{Give goal ratings sheet to P and ask them to follow the instructions.}

\textcolor{red}{Retry if rating 1 {\textless}5 or rating 2 {\textless} 5.}

\subsection{I-word generation}

\textit{In a few moments I'm going to ask you to generate some words which you associate with your
problem or concern. These must be single words and not phrases. The words can be English adjectives, nouns
(including names of people or places), verbs or any other word which is meaningful to you in relation to your problem
or concern. For example, if someone had an ongoing concern about an important relationship, which they had recently
felt that they should be managing better, they might choose the following words}

\begin{itemize}
\item {wedding}
\item {lonely}
\item {stressed}
\item {Cardiff}
\item {children}
\item {money}
\end{itemize}

\textit{Try to make each word directly relate to an aspect of the
problem or concern such as its causes, consequences or obstacles to
its resolution. Try not to simply choose synonyms for a \textbf{single
aspect} of the problem or concern. A simple way to do this is to choose
words which immediately bring the problem or concern to mind.}


\textit{ Here are some suggestions that  may help you to generate words.}

\begin{itemize}
\item {Think about the problem or concern -- what is it?}
\item {Focus on what it is about this problem/difficulty that bothers and troubles you.}
\item {Think about what's important about this difficulty in terms of your personal goals.}
\item {Focus on how the problem reflects a lack of progress on important personal goals.}
\item {Think about how the problem/difficulty is still \textbf{unresolved}.}
\item {Concentrate on the aspects of the problem that reflect unfinished business.}
\item {Focus on the aspects of the difficulty that \textbf{repeatedly come to mind}.}
\item {Think about any related concerns and unresolved issues that this problem reminds you of.}
\end{itemize}

\textit{Now dwell on your current problem or concern, in the way that
you would usually dwell on and ruminate about unresolved concerns. As
you do this, notice any words, images or emotions that you associate
with your problem or concern. Don't think too much, try to just go with
whatever first comes to mind. Write down these words whenever they come
to mind. Try to generate a minimum of 6 and a maximum of 10 words.}


\textbf{Give P I-word sheets and allow them time to read it.}

[\textcolor[rgb]{0.0,0.5019608,0.0}{Time 4 minutes}] if I-words incomplete

\textit{Do you just need a couple more minutes to complete the words or
would you like me to repeat some of the instructions to help you finish
the list?}

{Based on response, repeat some or all of generation instructions.}

[\textcolor[rgb]{0.0,0.5019608,0.0}{Time 3 minutes}] or if P completely blocked

Offer the option to generate a different goal and restart
procedure. \textbf{STOP} if P doesn't want to do this and can't generate
6 words with or without generating an alternative goal.

\textit{Now choose the 6 words that would be most likely to cause you to ruminate about this problem.}

[These 6 words are 'chosen words', additional words generated but not selected are 'spare words'.]

\subsection{I-word adjustment procedure}

\begin{center}
\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{|m{6.309cm}|m{1.7839999cm}|m{7.228cm}|}
\hline
{\selectlanguage{english}\bfseries\color[rgb]{0.0,0.0,0.039215688} Word type} &
{\selectlanguage{english}\bfseries\color[rgb]{0.0,0.0,0.039215688} Action} &
{\selectlanguage{english}\bfseries\color[rgb]{0.0,0.0,0.039215688} Suggestion}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} \foreignlanguage{english}{Proper noun, len {\textless}= 10}} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} ACCEPT} &
~
\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} Word with stem related to N-word} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} REJECT} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} \ Related N-word. \ }\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} Word present in MRC db, len {\textless}= 10} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} ACCEPT} &
~
\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} Word stem present in MRC db, len {\textgreater}= 10} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} REJECT} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} Generate synonyms\footnotemark{}\footnotemark{} (try
semantically related stems) or contractions.}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} Plural} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} REJECT} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} Singular form.}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} Acronyms or hyphenation} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} REJECT} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} Generate synonyms.}\\\hline
\end{supertabular}
\end{center}
\addtocounter{footnote}{-2}
\stepcounter{footnote}\footnotetext{
\begin{itemize}
\item {\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688}
\url{http://www.thesaurus.com/}}
\end{itemize}
}
\stepcounter{footnote}\footnotetext{
\begin{itemize}
\item {\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688}
\url{https://en.wiktionary.org/wiki/Wiktionary:Wikisaurus}}
\end{itemize}
}

{\textup{For each REJECT chosen word}}

\textit{Can you think of single words with the same, or similar meanings in relation to this problem?}

or

\textit{Can you think of a more general word than \textup{X} that has
the same, or similar meaning for you in relation to this problem?}


\textup{Re-validate synonyms generated by participant. [if ACCEPT chosen words {\textless} 6] Repeat.}

\textup{For each remaining REJECT chosen word}

\textit{Would \textup{ Y [researcher generated alternatives]} have the same or similar meaning for you as \textup{X
} in relation to this problem?}

\textup{[if ACCEPT chosen words {\textless} 6] Replace REJECT chosen words with any spare
ACCEPT words.}

[if words {\textless} 6 and spare REJECT words] Validate spare REJECT words and replace REJECT chosen words with any new
spare ACCEPT words.

[if words {\textless} 6] FAIL!

\subsection{I-word ratings}

{Give I-word ratings sheet to P and ask them to follow the instructions.}

\subsection{Pre-validated alternative words}

\begin{center}
\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{|m{7.76cm}|m{7.76cm}|}
\hline
{\selectlanguage{english}\bfseries\color[rgb]{0.0,0.0,0.039215688} I-word} &
{\selectlanguage{english}\bfseries\color[rgb]{0.0,0.0,0.039215688} Validated suggestions}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} PhD} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} DOCTORATE, THESIS}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} worry} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} WORRIED}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} responsibility} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} RESPONSIBLE}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} negative-equity} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} DEBT}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} ignominy} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} DISGRACE}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} repossession} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} HOUSING}\\\hline
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} radiotherapy} &
{\selectlanguage{english}\color[rgb]{0.0,0.0,0.039215688} TREATMENT}\\\hline
\end{supertabular}
\end{center}
