\subsection{Your GP}

If you have been experiencing low mood most of the day for more than
a few days, you should consider consulting your GP, who can provide
professional guidance and help. You can contact your GP to arrange an
appointment, or in an emergency. Most GP surgeries will connect you to an
out-of-hours service if you call outside office hours needing help. If
you are a student you can contact the Exeter University Student Health
Centre, whether or not you are currently registered there.

\begin{itemize}
  \item Streatham Campus: Student Health Centre, Reed Mews: (01392) 676606 or x 4414
  \item St Luke's Campus: Heavitree Health Practice, Heavitree Health Centre: (01392) 211511
  \item At other times during vacation contact the St Thomas Health Centre: (01392) 676676
\end{itemize}

\subsection{University of Exeter Wellbeing Service}

The Wellbeing Service is available free of charge to all students,
full-time, part-time, undergraduate and postgraduate.  Because student
life can be stressful, the Wellbeing Service is there to provide
confidential help and support. We aim to help students cope more
effectively with any personal problems or emotional difficulties that
may arise during their time at University.

Telephone: (01392) 724381\newline
Or book an appointment via the website: \url{http://www.exeter.ac.uk/wellbeing/appointments/}\newline
Student Wellbeing Service\newline
Reed Mews Wellbeing Centre\newline
Streatham Drive\newline
Exeter EX4 4QP

\subsection{Voice (University of Exeter)}

Voice is a student-run listening and information service, run by students
for fellow students at the University of Exeter and is available from
8pm to 8am every night during term time. It is completely confidential,
anonymous and prejudice-free, which means you can call with the confidence
of knowing you can discuss anything you want without being judged.

Telephone (8pm -- 8am): 4000 (internal, free of charge)\newline
External: (01392) 72400\newline
Email: \href{mailto:exetervoice@googlemail.com}{exetervoice@googlemail.com}\newline
Website: \url{http://www.exeterguild.org/voice/}

\subsection{Exeter Samaritans}

Samaritans provides confidential emotional support, 24 hours a day for
people who are experiencing feelings of distress or despair. Samaritans
are there if you're worried about something, feel upset or confused,
or you just want to talk to someone.

10 Richmond Road\newline
Exeter\newline
Devon\newline
EX4 4JA (open daily 10.30am -- 9.30pm)

24 hour telephone helpline: 01392 411711 (Exeter branch) / 08457 909090 (national)\newline
Email: \href{mailto:jo@samaritans.org}{jo@samaritans.org}\newline
Website: \url{http://www.samaritans.org/branches/samaritans-exeter-mid-east-devon}

\subsection{Depression Alliance}

Depression Alliance are a charity working to relieve and to prevent
depression by providing information, support and understanding. Depression
Alliance offer a range of publications and self-help groups.

Depression Alliance\newline
20 Great Dover Street\newline
London\newline
SE1 4LX\newline
Telephone: 0845 123 23 20 (for an information pack only)\newline
Email: \href{mailto:information@depressionalliance.org}information@depressionalliance.org\newline
Website: \url{http://www.depressionalliance.org/}
